---
title: "20220816_Psychometrics"
author: "Sidhant Chaudhary"
date: Sys.Date()
format: pdf
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r setup}
#| include: false
knitr::opts_chunk$set(message = F, warning = F,echo = TRUE)

# load packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, tidytuesdayR, skimr, conflicted) 

# conflicts: identical function names from different packages
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")

update_geom_defaults("rect", list(fill = "midnightblue", alpha = 0.8))
update_geom_defaults("line", list(color = "midnightblue", alpha = 0.8))
theme_set(theme_bw())
```

# Reading the datasets

```{r}
# uncomment to download data
tuesdata <- tidytuesdayR::tt_load('2022-08-16')
characters <- tuesdata$characters %>% janitor::clean_names()
myers_briggs <- tuesdata$myers_briggs %>% janitor::clean_names()
psych_stats <- tuesdata$psych_stats %>% janitor::clean_names()
```

```{r}
skim(characters)
skim(myers_briggs)
skim(psych_stats)
```

So, I will not be using the Myers Briggs data but only the characters data that is interesting to me.

# Let's explore the data

I think I will be filtering for the shows that I enjoyed in the past.

```{r}

characters %>%
  mutate(uni_name = str_replace_all(uni_name, " ", "_")) %>%
  #mutate(uni_name = str_to_lower(uni_name)) %>%
  select(uni_name) %>%
  unique() %>% print(n = Inf)

int_shows <- c("Friends", 
               "How_I_Met_Your_Mother", 
               "Game_of_Thrones", 
               "The_Office", 
               "The_Big_Bang_Theory",
               "Ozark",
               "Marvel_Cinematic_Universe",
               "Modern_Family",
               "Sherlock",
               "Brooklyn_Nine-Nine",
               "Breaking_Bad",
               "Dexter"
               )

# let combine and filter the datasets only for the interesting (to me) shows
char_psych <-
  characters %>%
  left_join(psych_stats, by = c("uni_id", "uni_name", "id" = "char_id", "name" = "char_name")) %>%
  mutate(uni_name = str_replace_all(uni_name, " ", "_")) %>% 
  filter(uni_name %in% int_shows) %>%
  mutate_if(is.character, factor) %>%
  select(uni_name, uni_id, name, id, notability, question, personality, avg_rating, rank, rating_sd, number_ratings)
```

# Exploring the combined dataset

```{r}
char_psych %>%
  group_by(personality) %>% count %>% view()

# Notability
char_psych %>%
  select(name, notability, uni_name) %>%
  distinct(name, notability, .keep_all = T ) %>%
  ggplot(aes(notability, fct_reorder(name, notability))) +
  geom_col() +
  scale_x_continuous(limits = c(0,100), expand = c(0,0), 
                     labels = scales::percent_format(scale = 1)) + 
  facet_wrap(~uni_name, scales = "free_y") + 
  labs(title = "Notability of various characters per show",
       x = "Notability", y = "Name of the character") 

# 
char_psych %>%
  filter(uni_name == "Breaking_Bad") %>%
  group_by(personality) %>% count()
```

-   **Notability trait** tells us how known a character is to general public and it follows the expectation per show.
-   

# Looking at the anti-hero characters across universes

Specifically, I am interested in exploring how similar the personality traits of below-mentioned characters are:

1.  Walter White
2.  Mike Ehrmantraut
3.  Gus Fring
4.  Saul Goodman
5.  Dexter Morgan
6.  Tyrion Lannister
7.  Jamie Lannister
8.  Marty Byrde
9.  Wendy Byrde
10. Ruth Langmore
11. Darlene Snell

```{r}

```
